\documentclass[a4paper]{article}
\usepackage[notheorems]{beamerarticle}

\input{../preamble}

%\def\solution {1}


\title{Table To Picture} 
\author{Christos Dimitrakakis}
\begin{document}
\maketitle

{\Large Student name:} \vspace{0.5em} \hrule \vspace{1em}

The purpose of this assignment is for you to create a graphic that
demonstrates something interesting about a data table found on the
web.  Please provide as precise and concise answers as possible. This
assignment is \textbf{graded}. You are \emph{encouraged} to discuss
the assignment with other students in a group. However each student
must prepare their own \emph{individual} report.  Please submit your
answers on \emph{moodle.}

\begin{exercise}
  \begin{enumerate}
  \item Find a data table on the internet. 
  \item Write a short description of the data on the table.
  \item Create one or two plots of your choice, summarising the data on the table.
  \item Explain what the graph shows about the data.
  \item Try and draw some conclusions or generalisations from the graph.
  \end{enumerate}
\end{exercise}

\begin{example}
  \begin{enumerate}
  \item Use the world records data for 100m/400m/1500m or some other distance.
  \item Explain what the records show.
  \item Show how the world record changes over time for men and women,
    with different colours. Be sure to plot records with the x axis
    showing time.
  \item Draw regression lines over the world record graph: the records reduce over time.
  \item It is not logically possible to expect the times to reduce linearly with time! Is there a fundamental limit? How can the data be best explained? Is human performance constant over time, and records are falling due to random chance? Is human performance slowly increasing over time?
  \end{enumerate}
\end{example}


\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
